\titletext{}

### 2021-07-09 manuscript/include/clust_summ.tex
Finished proofing

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Jul 15, 2020 - 09:38:19
\begin{table}[!htbp] \centering 
  \caption{Description of the biogeographical clusters to which each plot in the study was assigned. Indicator species were generated using Dufrene-Legendre indicator species analysis \citep{Dufrene1997} implemented with \texttt{indval()} from the \texttt{labdsv} R package \citep{labdsv} and represent species which define the given cluster. Dominant species were identified by choosing the species with the largest mean plot level proportional AGB within each cluster. Numeric values of species richness, stems ha\textsuperscript{-1} and AGB represent medians and interquartile ranges (75th percentile - 25th percentile).} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Dominant species} & {Indicator species} & {n} & \multicolumn{1}{p{2cm}}{\centering Species\\Richness} & \multicolumn{1}{p{2.5cm}}{\centering Stem density\\(stems ha\textsuperscript{-1})} & \multicolumn{1}{p{2cm}}{\centering AGB\\(t ha\textsuperscript{-1})} \\
\hline \\[-1.8ex] 
Core miombo & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Brachystegia spiciformis} \\\textit{Julbernardia paniculata} \\\textit{Brachystegia boehmii} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Parinari curatellifolia} \\\textit{Uapaca kirkiana} \\\textit{Brachystegia spiciformis} \end{tabular} & 523 & 20(16.9) & 204(142.5) & 44.2(36.11) \\ 
\hline
ex-Acacia & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Spirostachys africana} \\\textit{Senegalia burkei} \\\textit{Senegalia nigrescens} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Euclea racemosa} \\\textit{Vachellia nilotica} \\\textit{Spirostachys africana} \end{tabular} & 188 & 12(10.3) & 181(166.5) & 54.5(61.33) \\ 
\hline
Mopane & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \\\textit{Androstachys johnsonii} \\\textit{Kirkia acuminata} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{\textit{Colophospermum mopane}} \\\textit{Psuedolachnostylis maprouneifolia} \\\textit{Lannea discolor} \end{tabular} & 58 & 10(10.2) & 186(125.6) & 42.7(32.83) \\ 
\hline
Sparse miombo / Baikiaea & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Baikiaea plurijuga} \\\textit{Burkea africana} \\\textit{Pterocarpus angolensis} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Burkea africana} \\\textit{Baikiaea plurijuga} \\\textit{Pterocarpus angolensis} \end{tabular} & 466 & 12(13.7) & 178(129.5) & 36.9(26.98) \\ 
\hline
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Jul 15, 2020 - 09:38:19
\begin{table}[!htbp] \centering 
  	\caption{Description of the biogeographical clusters to which each plot in the study was assigned. Indicator species were generated using Dufrene-Legendre indicator species analysis \citep{Dufrene1997} implemented with \texttt{indval()} from the \texttt{labdsv} R package \citep{labdsv} and represent species which define the given cluster. Dominant species were identified by choosing the species with the largest mean plot level proportional AGB (Above-Ground woody Biomass) within each cluster. N = number of plots in cluster. Numeric values of species richness, stems ha\textsuperscript{-1} and AGB represent medians and interquartile ranges (75th percentile - 25th percentile).} 
  \label{clust_summ} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Dominant species} & {Indicator species} & {N} & \multicolumn{1}{p{2cm}}{\centering Species\\Richness} & \multicolumn{1}{p{2.5cm}}{\centering Stem density\\(stems ha\textsuperscript{-1})} & \multicolumn{1}{p{2cm}}{\centering AGB\\(t ha\textsuperscript{-1})} \\
\hline \\[-1.8ex] 
Core miombo & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Brachystegia spiciformis} \\\textit{Julbernardia paniculata} \\\textit{Brachystegia boehmii} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Parinari curatellifolia} \\\textit{Uapaca kirkiana} \\\textit{Brachystegia spiciformis} \end{tabular} & 523 & 20(16.9) & 204(142.5) & 44.2(36.11) \\ 
\hline
ex-Acacia & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Spirostachys africana} \\\textit{Senegalia burkei} \\\textit{Senegalia nigrescens} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Euclea racemosa} \\\textit{Vachellia nilotica} \\\textit{Spirostachys africana} \end{tabular} & 188 & 12(10.3) & 181(166.5) & 54.5(61.33) \\ 
\hline
Mopane & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Colophospermum mopane} \\\textit{Androstachys johnsonii} \\\textit{Kirkia acuminata} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{\textit{Colophospermum mopane}} \\\textit{Psuedolachnostylis maprouneifolia} \\\textit{Lannea discolor} \end{tabular} & 58 & 10(10.2) & 186(125.6) & 42.7(32.83) \\ 
\hline
Sparse miombo / Baikiaea & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Baikiaea plurijuga} \\\textit{Burkea africana} \\\textit{Pterocarpus angolensis} \end{tabular} & \begin{tabular}[c]{@{}c@{}c@{}} \textit{Burkea africana} \\\textit{Baikiaea plurijuga} \\\textit{Pterocarpus angolensis} \end{tabular} & 466 & 12(13.7) & 178(129.5) & 36.9(26.98) \\ 
\hline
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

### 2021-07-09 manuscript/include/struc_model_fit_clust_stats.tex
Finished proofing

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Jul 15, 2020 - 10:35:08
\begin{table}[!htbp] \centering 
  	\caption{Model fit statistics for SEMs investigating the effects of tree diversity and stem density on AGB (\autoref{struc_mod}). n = number of plots in cluster, $\chi^{2}$ = Chi-squared fit statistic, DoF = model degrees of freedom, CFI = Comparative Fit Index, TLI = Tucker-Lewis Index, RMSEA = Root Mean Square Error of Approximation, $R^{2}$ AGB = R-squared of AGB (Above-Ground Biomass).} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{0pt}} cccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {n} & {$\chi^{2}$} & {DoF} & {CFI} & {TLI} & {RMSEA} & {$R^{2}$ AGB} \\
\hline \\[-1.8ex] 
Core miombo & 523 & 78.670 & 6 & 0.904 & 0.759 & 0.140 & 0.490 \\ 
ex-Acacia & 188 & 9.570 & 6 & 0.952 & 0.879 & 0.130 & 0.830 \\ 
Mopane & 58 & 19.880 & 6 & 0.834 & 0.584 & 0.240 & 0.510 \\ 
Sparse miombo / Baikiaea & 466 & 43.870 & 6 & 0.914 & 0.784 & 0.130 & 0.580 \\ 
All & 1235 & 91.380 & 6 & 0.937 & 0.843 & 0.120 & 0.490 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Wed, Jul 15, 2020 - 10:35:08
\begin{table}[!htbp] \centering 
  	\caption{Model fit statistics for Structural Equation Models investigating the effects of tree diversity and stem density on AGB (\autoref{struc_mod}). N = number of plots in cluster, $\chi^{2}$ = Chi-squared fit statistic, DoF = model degrees of freedom, CFI = Comparative Fit Index, TLI = Tucker-Lewis Index, RMSEA = Root Mean Square Error of Approximation, $R^{2}$ AGB = R-squared of AGB (Above-Ground Biomass).} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{0pt}} cccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {N} & {$\chi^{2}$} & {DoF} & {CFI} & {TLI} & {RMSEA} & {$R^{2}$ AGB} \\
\hline \\[-1.8ex] 
Core miombo & 523 & 78.670 & 6 & 0.904 & 0.759 & 0.140 & 0.490 \\ 
ex-Acacia & 188 & 9.570 & 6 & 0.952 & 0.879 & 0.130 & 0.830 \\ 
Mopane & 58 & 19.880 & 6 & 0.834 & 0.584 & 0.240 & 0.510 \\ 
Sparse miombo / Baikiaea & 466 & 43.870 & 6 & 0.914 & 0.784 & 0.130 & 0.580 \\ 
All & 1235 & 91.380 & 6 & 0.937 & 0.843 & 0.120 & 0.490 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

### 2021-07-09 manuscript/regional_befr_manuscript.tex
Finished proofing

% Define page geometry
\usepackage{geometry}
\geometry{left=2.2cm,
	right=2.2cm,
	top=2.2cm,
	bottom=2cm}
\parskip 0.15cm
\setlength{\parindent}{0cm}
\renewcommand{\baselinestretch}{1.5}
\usepackage{pdflscape}
\usepackage[document]{ragged2e}

% Set font
\usepackage[T1]{fontenc}

\usepackage{framed}

\usepackage{setspace}
\doublespacing

% Image handling
\usepackage{graphics} % Insert images easily
\usepackage{graphicx} % Extended image support

@@

\graphicspath{ {img/} }
\usepackage{float} % Graphics placement [H] [H!] arguments
\usepackage{subfig} % Compound figures

% Tables
\usepackage{multirow}
\usepackage{longtable}

% Bibliography management
\usepackage[UKenglish]{babel}
\usepackage[natbibapa]{apacite}
\bibliographystyle{apacite}

% Text formatting
\usepackage{url} % Allow nice formatting of URLs in text

\usepackage{enumerate} % Enumerated lists

\usepackage{lineno} % Line numbers

\usepackage{textcomp}
\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}} % Command for a good tilde

\usepackage{siunitx}
\usepackage{amsmath}

\usepackage{xcolor}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{#1}}}  % \todo{NOTE TO SELF WRITTEN IN RED}

\input{code_format}

\usepackage[breaklinks]{hyperref}
\definecolor{links}{RGB}{0,0,0}
\hypersetup{
	breaklinks,
	colorlinks=true,
	linkcolor=links,
	anchorcolor=links,
	citecolor=links,
	filecolor=links,
	menucolor=links,
	runcolor=links,
	urlcolor=links,
	pdfauthor={John L. Godlee}
}
\def\subsectionautorefname{section}
\def\subsubsectionautorefname{section}
% \usepackage{biblatex}

\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{calc,arrows,positioning,shapes,shapes.gates.logic.US,trees}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{fmtcount}

\linenumbers
\linespread{1.25}

\usepackage[clean]{revdiff}

\newcommand{\titletext}{Structural diversity and tree density drives variation in the biodiversity-ecosystem function relationship of woodlands and savannas}

\input{include/n_plots}
\input{include/hull_cover}
\input{include/path_coef_struc}
\input{include/path_coef_full}
\input{include/corr_coef}
\input{include/dens_stats}
\input{include/perc_small_agb.tex}
\input{include/zam.tex}

@@

{\Large{Title: \titletext{}}}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{concept.drawio}
	\caption{Conceptual Directed Acyclic Graph (DAG) showing the theoretical relationships between environmental factors, tree species diversity, tree structural diversity, stem density, and AGB. Hypothesised paths of causation are depicted as arrows from predictor to response. Open arrow heads track the direction of each arrow along its path.}
	\label{con_mod}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.6\textwidth]{corr_mat}
	\caption{Correlation matrix of standardised observed variables used in the SEMs, with Pearson correlation coefficients ($r$) coloured according to sign ($+$ve red, $-$ve blue) and shaded by strength of correlation. Correlation coefficients marked by a circle indicate that the 95\% confidence interval of $r$ overlapped zero. Colours of variable names group them into latent variables used in the SEMs: red = soil fertility, blue = disturbance, turquoise = water availability, green = tree species diversity, purple = tree structural diversity. See Table S1 for a full assessment of correlation fit statistics.}
	\label{corr_mat}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.5\textwidth]{struc.drawio}
	\caption{Path diagram with regression coefficients for the tree diversity SEM, including plots from all vegetation clusters. Latent variables are shown as circles while observed variables are shown as rectangles. Standardised path coefficients are shown as solid arrows pointing from predictor to response with the effect size of the path coefficient expressed in terms of standard deviations on the latent variable response scale. The observed variables that inform the latent variables are connected by dotted arrows, and observed variables with loadings set to one are connected by dashed arrows. Measurement errors of exogenous variables are omitted for clarity.}
	\label{struc_mod}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{struc_model_slopes_all}
	\caption{Unstandardised path coefficients for the effects of tree diversity on AGB, mediated by the effect of stand structural diversity. Path coefficients are $\pm$1 standard error. Path coefficients where the interval (standard error) does not overlap zero are considered to be significant effects.}
	\label{struc_model_slopes_all}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.8\textwidth]{sem_struc_stems_ha}
	\caption{Line plots showing the variation in SEM path coefficients across datasets with different mean stem density. Smoothed lines are loess curves with $\pm1$ standard error shaded bars. AGB = Above-Ground woody Biomass, arrows in plot titles indicate causal paths in SEM models. Where multiple arrows are present, as in c), this indicates an indirect pathway via an intermediate variable.}
	\label{sem_struc_stems_ha}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{full.drawio}
	\caption{Path diagram with regression coefficients for the SEM incorporating environmental covariates and tree species and structural diversity across all five vegetation types. Latent variables are shown as circles while observed variables are shown as rectangles. Standardised path coefficients are shown as solid arrows pointing from predictor to response, with the effect size of the path coefficient expressed in terms of standard deviations on the latent variable response scale. Observed variables that inform the latent variables are connected by dotted arrows, observed variables with loading set to one are connected by dashed arrows. Measurement errors of exogenous variables are omitted for clarity.}
	\label{full_mod}
\end{figure}
\newpage{}

@@

This work is funded by a NERC E3 Doctoral Training Partnership PhD studentship at the University of Edinburgh (John L. Godlee, Grant No. NE/L002558/1). The data for this study was contributed by a number of independently funded projects and was assembled and prepared by SEOSAW (A Socio-Ecological Observatory for Southern African Woodlands, \url{https://seosaw.github.io}), an activity of the Miombo Network and a NERC-funded project (Grant No. NE/P008755/1). Revisions of the SEOSAW dataset were funded by SavannaChange, a GCRF/University of Edinburgh funded project. We thank all data providers and the field assistance they received when collecting plot data. JMBC was supported by the Natural Environment Research Council (Agreement PR140015 between NERC and the National Centre for Earth Observation).

@@

JG and KD conceived the study. JG conducted data analysis, data management for further versions of the SEOSAW dataset, and wrote the manuscript. CR conceived the SEOSAW database and conducted data management for earlier versions of the SEOSAW dataset. JG, CR, DB, JMBC, MF, RH, EM, SS, HT, HT, MB, MW, and KD contributed to manuscript revisions. JG, CR, SB, VC, JPGMC, DD, MF, FG, SM, IM, AM, RR, NR, AS, SS, JT, JW, MB, and MW contributed to experimental design, field data collection, data preparation and data management of parts of the dataset used in this study.

@@

The data that support the findings of this study are available on request from the corresponding author. The data are not publicly available at the time of submission due to privacy restrictions regarding plot locations. An anonymised version will be made available in a data repository following review.

\bibliography{regional_befr_manuscript.bib}

>>>>

% Page geometry
\usepackage{geometry}
\geometry{left=2.2cm,
	right=2.2cm,
	top=2.2cm,
	bottom=2cm}
\parskip 0.2cm
\setlength{\parindent}{0cm}
\usepackage{pdflscape}
\usepackage{framed}
\usepackage{lineno} 
\linenumbers

% Text 
\usepackage[T1]{fontenc}
\linespread{1.25}
\usepackage{siunitx}

% Images 
\usepackage{graphics} % Insert images easily
\usepackage{graphicx} % Extended image support
\usepackage{float} % Graphics placement [H] [H!] arguments

@@

\graphicspath{ {img/} }

% Bibliography 
\usepackage[UKenglish]{babel}
\usepackage{csquotes}
\usepackage[natbib, 
	style=authoryear, 
	uniquename=false, 
	uniquelist=false,
	maxcitenames=2, 
	mincitenames=1, 
	minbibnames=10, 
	maxbibnames=10, 
	backend=biber]{biblatex}
\renewcommand*\finalnamedelim{\addspace\&\space}
\addbibresource{regional_befr_manuscript.bib}

% Cross references and hyperlinks
\usepackage{xcolor}
\usepackage{url} 
\usepackage[breaklinks]{hyperref}
\definecolor{links}{RGB}{0,0,0}
\hypersetup{
	breaklinks,
	colorlinks=true,
	linkcolor=links,
	anchorcolor=links,
	citecolor=links,
	filecolor=links,
	menucolor=links,
	runcolor=links,
	urlcolor=links,
	pdfauthor={John L. Godlee}
}
\def\subsectionautorefname{section}
\def\subsubsectionautorefname{section}

% External files
\input{include/n_plots}
\input{include/hull_cover}
\input{include/path_coef_struc}
\input{include/path_coef_full}
\input{include/corr_coef}
\input{include/dens_stats}
\input{include/perc_small_agb.tex}
\input{include/zam.tex}

@@

{\textbf{Title: Structural diversity and tree density drives variation in the biodiversity-ecosystem function relationship of woodlands and savannas}}

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{concept.drawio}
\caption{Conceptual Directed Acyclic Graph (DAG) showing the theoretical relationships between environmental factors, tree species diversity, tree structural diversity, stem density, and AGB (Above-Ground Woody Biomass). Hypothesised paths of causation are depicted as arrows from predictor to response. Open arrow heads track the direction of each arrow along its path.}
	\label{con_mod}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.6\textwidth]{corr_mat}
	\caption{Correlation matrix of standardised observed variables used in the SEMs (Structural Equation Models), with Pearson correlation coefficients ($r$) coloured according to sign ($+$ve red, $-$ve blue) and shaded by strength of correlation. Correlation coefficients marked by a circle indicate that the 95\% confidence interval of $r$ overlapped zero. Colours of variable names group them into latent variables used in the SEMs: red = soil fertility, blue = disturbance, turquoise = water availability, green = tree species diversity, purple = tree structural diversity. See Table S1 for a full assessment of correlation fit statistics.}
	\label{corr_mat}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.5\textwidth]{struc.drawio}
	\caption{Path diagram with regression coefficients for the tree diversity SEM (Structural Equation Model), including plots from all vegetation clusters. Latent variables are shown as circles while observed variables are shown as rectangles. Standardised path coefficients are shown as solid arrows pointing from predictor to response with the effect size of the path coefficient expressed in terms of standard deviations on the latent variable response scale. The observed variables that inform the latent variables are connected by dotted arrows, and observed variables with loadings set to one are connected by dashed arrows. Measurement errors of exogenous variables are omitted for clarity.}
	\label{struc_mod}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{struc_model_slopes_all}
	\caption{Unstandardised path coefficients for the effects of tree diversity on AGB (Above-Ground Woody Biomass), mediated by the effect of stand structural diversity. Path coefficients are $\pm$1 standard error. Path coefficients where the interval (standard error) does not overlap zero are considered to be significant effects.}
	\label{struc_model_slopes_all}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=0.8\textwidth]{sem_struc_stems_ha}
	\caption{Line plots showing the variation in SEM (Structural Equation Model) path coefficients among latent variables, across datasets with different mean stem density. Smoothed lines are loess curves with $\pm1$ standard error shaded bars. AGB = Above-Ground woody Biomass. Arrows in plot titles indicate causal paths in SEM models. Where multiple arrows are present, as in c), this indicates an indirect pathway via an intermediate variable. a) shows the direct effect of species diversity on structural diversity. b) and d) show the direct effects of species diversity and structural diversity on AGB, respectively. c) shows the indirect effect of species diversity on AGB via structural diversity. e) shows the total effect of species diversity on AGB, incorporating both the direct effect and the indrect effect via structural diversity.}
	\label{sem_struc_stems_ha}
\end{figure}
\newpage{}

\begin{figure}[H]
\centering
	\includegraphics[width=\textwidth]{full.drawio}
	\caption{Path diagram with regression coefficients for the SEM (Structural Equation Model) incorporating environmental covariates and tree species and structural diversity across all five vegetation types. Latent variables are shown as circles while observed variables are shown as rectangles. Standardised path coefficients are shown as solid arrows pointing from predictor to response, with the effect size of the path coefficient expressed in terms of standard deviations on the latent variable response scale. Observed variables that inform the latent variables are connected by dotted arrows, observed variables with loading set to one are connected by dashed arrows. Measurement errors of exogenous variables are omitted for clarity.}
	\label{full_mod}
\end{figure}
\newpage{}

@@

This work is funded by a NERC E3 Doctoral Training Partnership PhD studentship at the University of Edinburgh (John L. Godlee, Grant No. NE/L002558/1). The data for this study was contributed by a number of independently funded projects and was assembled and prepared by SEOSAW (A Socio-Ecological Observatory for Southern African Woodlands, \url{https://seosaw.github.io}), an activity of the Miombo Network and a NERC-funded project (Grant No. NE/P008755/1). Revisions of the SEOSAW dataset were funded by SavannaChange, a GCRF/University of Edinburgh funded project. We thank all data providers and the field assistance they received in collecting plot data. JMBC was supported by the Natural Environment Research Council (Agreement PR140015 between NERC and the National Centre for Earth Observation).

@@

JLG and KGD conceived the study. JLG conducted data analysis, data management for further versions of the SEOSAW dataset, and wrote the manuscript. CMR conceived the SEOSAW database and conducted data management for earlier versions of the SEOSAW dataset. JLG, CMR, DB, ETAM, HGT, JMBC, KGD, MF, MW, MtB, RMH and SS contributed to manuscript revisions. JLG, AM, AS, AVC, CMR, DJD, FMG, IM, JJT, JPGMC, JW, MF, MtB, MW, NSR, RR, SJB, SM and SS contributed to experimental design, field data collection, data preparation and data management of parts of the dataset used in this study.

@@

An anonymised version of the data that support the findings of this study are available at this DOI: .

\printbibliography{}

### 2021-07-09 manuscript/si/si.tex
Finished proofing

\section{Appendix 1 - Frequency distribution of observed variables} \label{appendixa}

@@

\appendix{}
\section{Appendix 2 - Table of correlation fit statistics} \label{appendixb}

@@

\section{Appendix 3 - Bivariate relationships of model variables} \label{appendixc}

\begin{figure}[H]
\centering
	\includegraphics[width=0.9\textwidth]{bivar_lm}
	\caption{Bivariate scatter plots for each observed variable used in the SEMs, based on hypothesised paths of causality. Points are coloured according to vegetation type. A single linear regression is presented as a black line, which combines all vegetation types, separate loess trend lines are fitted for each vegetation type. An orange loess trend line is fitted for all the data. All data is standardised and variables are transformed where it was appropriate for analysis.}
	\label{bivar_lm}
\end{figure}

\section{Appendix 4 - Path coefficients for model incorporating environmental covariates} \label{appendixd}

>>>>

\documentclass[11pt,a4paper]{article}

% Define page geometry
\usepackage{geometry}
\geometry{left=2.2cm,
	right=2.2cm,
	top=2.2cm,
	bottom=2cm}
\parskip 0.2cm
\setlength{\parindent}{0cm}

% Set font
\usepackage[T1]{fontenc}

% Image handling
\usepackage{graphics} % Insert images easily
\usepackage{graphicx} % Extended image support
\usepackage{float} % Graphics placement [H] [H!] arguments

\makeatletter
	\g@addto@macro\@floatboxreset\centering % Automatically centre images (floats)
\makeatother

\graphicspath{ {img/} }

% Tables
\usepackage{longtable}

% Figure and table captions
\usepackage{caption}
\captionsetup[figure]{name={Fig.},labelsep=period}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

\begin{document}

{\Large{New Phytologist Supporting Information}}

{\textbf{Title: Structural diversity and tree density drives variation in the biodiversity-ecosystem function relationship of woodlands and savannas}}

John L. Godlee, Casey M. Ryan, David Bauman, Samuel J. Bowers, Joao M. B. Carreiras, Antonio Valter Chisingui, Joris P. G. M. Cromsigt, Dave J. Druce, Manfred Finckh, Francisco Maiato Gon\c{c}alves, Ricardo M. Holdo, Steve Makungwa, Iain M. McNicol, Edward T. A. Mitchard, Anderson Muchawona, Rasmus Revermann, Natasha Sofia Ribeiro, Abel Siampale, Stephen Syampungani, Jos\'{e} Jo\~{a}o Tchamba, Hemant G. Tripathi, Johannes Wallenfang, Mariska te Beest, Mathew Williams, Kyle G. Dexter

Article acceptance date: 1st July 2021

\section*{Figs S1 and S2 - Frequency distribution of observed variables} \label{appendixa}

@@

\appendix{}
\section*{Table S1 - Table of correlation fit statistics} \label{appendixb}

@@

\section*{Fig. S3 - Bivariate relationships of model variables} \label{appendixc}

\begin{figure}[H]
\centering
	\includegraphics[width=0.9\textwidth]{bivar_lm}
	\caption{Bivariate scatter plots for each observed variable used in the SEMs (Structural Equation Models), based on hypothesised paths of causality. Points are coloured according to vegetation type: green = Sparse miombo/Baikiaea, purple = Core miombo, blue = ex-Acacia, red = Mopane. The black line combines all vegetation types in a single linear regression, while loess trend lines are fitted for each vegetation type, separately. An orange loess trend line is fitted for all the data. All data is standardised to a mean of zero and a standard deviation of one. Variables are transformed where it was appropriate for analysis.}
	\label{bivar_lm}
\end{figure}

\section*{Fig. S4 - Path coefficients for model incorporating environmental covariates} \label{appendixd}
